---
title: "Interactive Sunburst Graphic for Metagenomic Analysis"
author: "Alejandro José Gómez García"
email: alejandrorex95@gmail.com
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_download: TRUE
    theme: united
  csl: apa.csl
---

## Necessary Package

The "sunburst" package provides functions to create interactive visualizations of sunburst diagrams. Sunburst diagrams are useful for displaying the hierarchical structure of data and how categories overlap.
```{r, warning=FALSE}
library(sunburstR)
```

To make an interactive phylogenetic tree plot with the SunburstR package
The data must be in csv and each taxonomic class to be classified must be separated by a hyphen (in the same column) and in another column the count

## Example of data type

```{r}
sun_all<-read.csv(choose.files(), header = FALSE, sep = ";",stringsAsFactors = FALSE)
head(sun_all)
```

### Sunburst Graphic

First, we will plot all identified individuals, regardless of the level to which they have been identified.
```{r, warning=FALSE}
sunburst(sun_all,count = TRUE, sumNodes = FALSE)
```

```{r}
sun_species<-read.csv(choose.files(), header = FALSE, sep = ";",stringsAsFactors = FALSE)
```

### Sunburst Graphic with only species

In this case we will only graph the individuals that have been identified up to the species level to compare with the previous graph.
```{r, warning=FALSE}
sunburst(sun_species,count = TRUE)
```


